Devphotodraw_main_anlayses

### 2021-06-17 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
updated main analysis script

---
title: "Devphotodraw_main_anlayses"
author: "Bria Long"
date: "6/16/2021"
output: html_document
---
# Preprocessing
## Load libraries
```{r}
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)

@@

@@

## Remove 3-way interaction
No interactions with site are significant, removing from main effects structure
When 3 way interaction is removed, still can't add back more random slopes.
```{r}

@@

```{r}
summary(full_model_no_int)
```

>>>>

---
title: "Devphotodraw_main_anlayses"
author: "Bria Long"
date: "6/16/2021"
output:
  html_document:
    toc: true
    theme: united
---
# Preprocessing
## Load libraries
```{r}
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)

@@

```{r}
by_category <- humans_merged %>%
  group_by(category) %>%
  summarize(humans_pc = mean(num_correct), model_pc = mean(correct_or_not, na.rm=TRUE))

ggplot(by_category, aes(x=model_pc, y=humans_pc, label=category)) +
  geom_point() +
  geom_smooth(method='lm') +
  ylab('human recognition') +
  xlab('model recognition') +
  theme_few() +
  ggrepel::geom_label_repel()
```

@@

### Remove 3-way interaction
No interactions with site are significant, removing from main effects structure
When 3 way interaction is removed, still can't add back more random slopes.
```{r}

@@

### Add back site*condition
```{r}
with_site_condition <- glmer(correct_or_not ~ condition*scale(age_numeric)+condition*site +
                        (1 | unique_ids) +
                        (condition*scale(age_numeric) | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

summary(with_site_condition)

### Add back age*site
```{r}
with_age_site <- glmer(correct_or_not ~ condition*scale(age_numeric)+scale(age_numeric)*site +
                        (1 | unique_ids) +
                        (condition*scale(age_numeric) | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

summary(with_age_site)

## Add back both
```{r}

with_site_condition_and_site_age <- glmer(correct_or_not ~ condition*scale(age_numeric)+condition*site+scale(age_numeric)*site+
                        (1 | unique_ids) +
                        (condition*scale(age_numeric) | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

summary(with_site_condition_and_site_age)
```
